\huge Tor's Usability for Censorship Circumvention

### 2016-04-19 pets2017-paper/pets2017-paper.tex
Edits.

\section{Related Work} 
There have been three published user studies on Tor. Clark et~al.~\cite{clark2007usability} examined various deployment
options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and Foxyproxy, and found that none of them 
were satisfactory from a usability perspective. Fabian et~al.~\cite{fabian2010privately} show that Tor's added
latency~\cite{dingledine2009performance} causes users
to be frustrated, cancel requests more often, and prevents user adoption. 
Norcie et~al.~\cite{norcie2012eliminating} found found that 
64\% of users are unable to continue with installation or browsing at least once due to difficulties.

@@

Participants in E3, the most advanced censorship environment, were required to select a meek bridge (not the default) or to configure a custom bridge. After the first pluggable transport failed and even if the participants deduced that the source of the failed connection was a mis-configured bridge, the pluggable transport names only confused participants and caused odd behaviors. Participants chose transports at random, in order of the list starting from the default, in order of the list starting from the top, choosing familiar-sounding transports first (i.e. meek-amazon over fte), and choosing technical-sounding transports first (i.e. fte over meek-amazon).

>>>>

\section{Related Work} 
There have been three published user studies on Tor. Clark et~al.~\cite{clark2007usability} examined various deployment
options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and FoxyProxy, and found that none of them 
were satisfactory from a usability perspective. Fabian et~al.~\cite{fabian2010privately} show that Tor's added
latency~\cite{dingledine2009performance} causes users
to be frustrated, cancel requests more often, and prevents user adoption. 
Norcie et~al.~\cite{norcie2012eliminating} found found that 
64\% of users are unable to continue with installation or browsing at least once due to difficulties.

@@

Participants in E3, the most advanced censorship environment, were required to select a meek bridge (not the default) or to configure a custom bridge. After the first pluggable transport failed and even if the participants deduced that the source of the failed connection was a misconfigured bridge, the pluggable transport names only confused participants and caused odd behaviors. Participants chose transports at random, in order of the list starting from the default, in order of the list starting from the top, choosing familiar-sounding transports first (i.e. meek-amazon over fte), and choosing technical-sounding transports first (i.e. fte over meek-amazon).
